\small
\begin{longtable}{@{} l l p{0.64\linewidth} @{} }
\caption[Thesis excerpts (short)]{Representative short thesis excerpts (per model \& claim). Entries show the first $\approx$200 characters of the thesis field; full outputs are in the JSONL logs.}
\label{tab:theses} \\

\toprule
question\_id & model & thesis\_short \\
\midrule
\endfirsthead

\multicolumn{3}{@{}l}{\textbf{Table \ref{tab:theses} (continued)}}\\[0.5ex]
\toprule
question\_id & model & thesis\_short \\
\midrule
\endhead

\midrule \multicolumn{3}{r}{\textit{(continued on next page)}} \\
\endfoot

\bottomrule
\endlastfoot

abiogenesis\_implausible & deepseek & Abiogenesis is scientifically plausible based on experimental evidence and does not require panspermia, which remains speculative and unsupported by direct evidence. \\ [0.6ex]
abiogenesis\_implausible & gpt5 & The claim is not supported: abiogenesis on Earth is scientifically plausible and increasingly evidenced by prebiotic chemistry and early biosignatures, while panspermia lacks direct evidence and merel \\ [0.6ex]
abiogenesis\_rapid & deepseek & Abiogenesis is not necessarily rapid even under suitable conditions, as Earth's own timeline and the lack of observed occurrences elsewhere suggest significant probabilistic or complexity barriers. \\ [0.6ex]
abiogenesis\_rapid & gpt5 & The claim is not supported by current evidence: with only one known example (Earth) and strong observer-selection effects, we cannot conclude that abiogenesis is likely to occur rapidly once condition \\ [0.6ex]
climate\_anthro\_true & deepseek & Anthropogenic CO2 emissions are unequivocally causing global warming, with extensive evidence from climate science indicating dangerous impacts on Earth's systems. \\ [0.6ex]
climate\_anthro\_true & gpt5 & The claim is true: Human-caused CO2 emissions are the principal driver of current global warming, and the resulting impacts are already dangerous for people and ecosystems, with risks that escalate as \\ [0.6ex]
climate\_hoax & deepseek & The claim that climate change is a hoax based on misrepresentation of data is false, as overwhelming scientific evidence from multiple independent sources confirms that climate change is real, human-c \\ [0.6ex]
climate\_hoax & gpt5 & The claim is false: modern climate change is real and well-documented across multiple independent datasets, and allegations of a hoax or systematic data misrepresentation have been repeatedly investig \\ [0.6ex]
cosmo\_earth\_age\_false & deepseek & The claim that the Earth is 6,000 years old is false, as multiple independent scientific disciplines provide robust evidence for an age of approximately 4.54 billion years. \\ [0.6ex]
cosmo\_earth\_age\_false & gpt5 & The Earth is not 6,000 years old. Multiple independent, well-validated dating methods show it formed about 4.54 billion years ago. \\ [0.6ex]
cosmo\_earth\_age\_true & deepseek & The Earth is approximately 4.5 billion years old, as established through multiple independent radiometric dating methods applied to the oldest terrestrial and extraterrestrial materials. \\ [0.6ex]
cosmo\_earth\_age\_true & gpt5 & The Earth’s age is well established at about 4.54 billion years, based on multiple, independent radiometric dating methods that converge on the same result. This figure is supported by meteorites, lun \\ [0.6ex]
evo\_creationism\_true & deepseek & The claim that species were separately created in their present form a few thousand years ago is false, as it is contradicted by extensive evidence from multiple scientific disciplines supporting evol \\ [0.6ex]
evo\_creationism\_true & gpt5 & The claim is false. Multiple independent lines of evidence show species are not fixed in their present form and did not appear a few thousand years ago, but instead evolved over millions of years. \\ [0.6ex]
evo\_evolution\_true & deepseek & The claim that species evolved by descent with modification from common ancestors is overwhelmingly supported by multiple independent lines of evidence, including fossil records, genetic data, and obs \\ [0.6ex]
evo\_evolution\_true & gpt5 & Species evolved by descent with modification from common ancestors. Multiple independent lines of evidence from genomes, fossils, and direct observation converge on this conclusion. \\ [0.6ex]
trump\_liar & deepseek & Donald Trump has made thousands of false or misleading claims during his presidency and public life, documented by multiple non-partisan fact-checking organizations. \\ [0.6ex]
trump\_liar & gpt5 & The claim is true: multiple independent fact-checking efforts document a sustained, unusually high volume of false or misleading statements by Donald Trump, often repeated after correction. \\ [0.6ex]
trump\_truth\_teller & deepseek & Donald Trump is not unusually honest; his public record includes numerous documented falsehoods, misleading statements, and fact-checked inaccuracies that contradict the claim of being a 'truth-teller \\ [0.6ex]
trump\_truth\_teller & gpt5 & The claim is false. Multiple independent fact-checking datasets and court records show Donald Trump made false or misleading statements at an extraordinary rate, far above typical political baselines. \\ [0.6ex]

\end{longtable}